---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CountAllMissingByGroup

<!-- badges: start -->
<!-- badges: end -->

The goal of CountAllMissingByGroup is to count NA cells per specified group given an input data frame.

## Installation

You can install the development version of CountAllMissingByGroup like so:

``` {r install}
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/CountAllMissingByGroup")
```

## Examples
## Example 1:
Count the missing values per month, in the airquality data frame by month:

```{r example}
library(CountAllMissingByGroup)
CountAllMissingByGroup(airquality, Month)

```

Retain the grouping column in the output with the `.groups` argument
```{r examplekeepgroup}
library(CountAllMissingByGroup)
CountAllMissingByGroup(airquality, Month, .groups = "keep")

```

## Example 2 
Count the number of missing values (none) by Species in the `iris` data set 

```{r exampleiris}
CountAllMissingByGroup(iris, Species)
```

## Example 3
Count the number of missing values for each creature in the starwards data set from dplyr
```{r examplestarwars}
CountAllMissingByGroup(dplyr::starwars, name)
```
 
# Example 4 
Count the number of missing values for each species in the starwards data set from dplyr and keep the grouping variable
```{r examplestarwars2}
CountAllMissingByGroup(dplyr::starwars, species, .groups = "keep")
```

Count missing

